---
title: "Homework 6"
author: "Nihan Gencerliler"
date: "11/23/2019"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(modelr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 16, 
  fig.height = 12,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(10)
```

## Problem 1

Load and clean birthweight dataset:

```{r}
birthweight = 
read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
 mutate(babysex=fct_inseq(as.factor(babysex)),frace=fct_inseq(as.factor(frace)),
        malform = fct_inseq(as.factor(malform)), mrace = fct_inseq(as.factor(mrace)))
#glimpse(birthweight)
```

The number of missing values is `r sum(is.na(birthweight))`.

I started building my model by selecting predictors based on what is known about factors that influence birthweight. I chose gaweeks, wtgain, smoken, mrace based on the information [here](https://www.stanfordchildrens.org/en/topic/default?id=low-birthweight-90-P02382). Because gestational age is the most important predictor of birthweight, I plotted it against birthweight to see what the most appropiate fit  would be. The scatterplot suggests linearity, so I will model it as such:
```{r}
birthweight %>%
  ggplot(aes(x=gaweeks,y=bwt)) + 
  geom_point()
```
I then fit a model of birthweight with the four predictors that I selected. Because all of the predictors are  significant, none of them will be removed.
```{r}
fit1 = lm(bwt ~ gaweeks + wtgain + mrace + smoken, data = birthweight)
fit1 %>% 
  broom::tidy() %>%
  knitr::kable()
```

Plotting residuals against predicted values:
```{r}
modelr::add_residuals(birthweight, fit1) %>%
modelr::add_predictions(fit1)  %>%
ggplot(aes(x = pred, y = resid)) +  geom_point()
```

Model using length at birth and gestational age as predictors (main effects only):
```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = birthweight)
fit2 %>% 
  broom::tidy() %>%
  knitr::kable()
```

Model using head circumference, length, sex, and all interactions (including the three-way interaction) between these:
```{r}
fit3 = lm(bwt ~ bhead * blength * babysex, data = birthweight)
fit3 %>% 
  broom::tidy() %>%
  knitr::kable()
```
Cross-validation: 
```{r}
cv_df = 
  crossv_mc(birthweight, 100) 
cv_df = 
  cv_df %>% 
  mutate(fit1  = map(train, ~lm(bwt ~ gaweeks + wtgain + mrace + smoken, data = .x)),
         fit2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         fit3  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
         rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
         rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

## Problem 2

```{r results="hide"}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Create dataset with r-squared and log(beta0*beta1):

```{r}
bootstrap = 
weather_df %>%
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    tidy = map(models, broom::tidy),
    glance = map(models, broom::glance)) %>% 
  unnest(tidy) %>% 
  select(term,estimate,glance) %>%
  unnest(glance) %>%
  pivot_wider(names_from = "term",
              values_from = "estimate") %>%
  mutate(logbeta = log(`(Intercept)`*tmin))
```

The 95% confidence interval for r-squared is (0.894, 0.927):

```{r}
bootstrap %>%
    ggplot(aes(x = r.squared)) + geom_density()
bootstrap %>%
  pull(r.squared) %>%
quantile(probs = c(0.025,0.975)) %>%
  knitr::kable()
```


The 95% confidence interval for log(beta0*beta1) is (1.964, 2.060):

```{r}
bootstrap %>%
  ggplot(aes(x = logbeta)) + geom_density()
bootstrap %>%
  pull(logbeta) %>%
quantile(probs = c(0.025,0.975)) %>%
  knitr::kable()
```

The density plots created for both of these terms resemble normal distributions, as one would expect given the central limit theorem.

